### 2013-09-15 research/paper/results/results-2.3.tex
Sketch completed..

 Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because they scale with the natural frequency of the system. The effect of fixing $\zeta$ and increasing $U^*$ actually decreases the damping constant for a fixed free-stream velocity. ($U^*=\frac{U}{f \times D}$, $\zeta= \frac{c}{2 m \omega_n}$ ). Both these effects leads to the multiple lines that are horizontally transpose when $\zeta$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)). Therefore the effect of $\zeta$ essentially scales up the damping coefficient for a fixed $U^*$.

@@

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. c When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$. The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in \ref{fig:power_time_histories}. While the time average of both quantities are the same, instantaneously they are not. Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle. In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by using quasi-steady state model and numerical methods. The system is not frequency dependent but more dependent on the velocity amplitude of they system. It could be proven from the collapsed plots in terms of non-dimensionalised (using flow parameters) damping constant. By anaylizing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($c\rho\mathcal{A}U$) should be high, but not too high enough to hinder the induced angle of attack reaching the region of higher forcing. The reduction in power at low mass ratios was due to the fact that the instantaneous $P_t$ and $P_d$ are not the same. Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.

>>>>

 Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because the scale with the natural frequency of the system. The effect of fixing $\zeta$ and increasing $U^*$ actually decreases the damping constant for a fixed free-stream velocity. ($U^*=\frac{U}{f \times D}$, $\zeta= \frac{c}{2 m \omega_n}$ ). Both these effects leads to the multiple lines that are horizontally transpose when $\zeta$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)). Therefore the effect of $\zeta$ essentially scales up the damping coefficient for a fixed $U^*$.

@@

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. c When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$. The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in Fig.\ref{fig:power_time_histories}. While the time average of both quantities are the same, instantaneously they are not. Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle. In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by using quasi-steady state model and numerical methods. The system is not frequency dependent but more dependent on the velocity amplitude of the system. It could be proven from the collapsed plots in terms of non-dimensionalised (using flow parameters) damping constant. By anaylizing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($c\rho\mathcal{A}U$) should be high, but not too high enough to hinder the induced angle of attack reaching the region of higher forcing. The reduction in power at low mass ratios was due to the fact that the instantaneous $P_t$ and $P_d$ are not the same. Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.
